Modal type theory based on the intuitionistic epistemic logic

### 2018-01-17 article.tex
added some stuff

@@

\begin{proof}
  i) For $\beta$-reduction

@@

>>>>

We identify terminal objects. So $\mathcal{K}(\mathds{1}) = \mathds{1}$ and $\eta_{\mathds{1}} = id_{\mathds{1}}$ since $\mathcal{K}$ is an endofunctor.

@@

  i) For $\beta$-reduction

@@

ii) For $\eta$-reduction.

1) $[\![\Gamma \vdash {\bf pure \:} (\lambda x. M x) : {\bf K}(A \to B)]\!] = [\![\Gamma \vdash {\bf pure \:} M : {\bf K}(A \to B)]\!]$.

$\begin{array}{lll}
&[\![\Gamma \vdash {\bf pure \:} (\lambda x. M x) : {\bf K}(A \to B)]\!] = & \text{By interpetation} \\
&\eta_{[\![B]\!]^{[\![A]\!]}} \circ \Lambda(\epsilon \circ [\![M]\!] \times id_{[\![A]\!])}& \text{Exponentiation property} \\
&\eta_{[\![B]\!]^{[\![A]\!]}} \circ [\![M]\!] = & \text{By interpretation} \\
&[\![\Gamma \vdash {\bf pure \:} M : {\bf K}(A \to B)]\!]&
\end{array}$

2) $[\![\Gamma \vdash {\bf pure \:} \langle \pi_1 M, \pi_2 M \rangle : {\bf K}(A \times B)]\!] = [\![\Gamma \vdash {\bf pure \:} M : {\bf K}(A \times B)]\!]$

$\begin{array}{lll}
&[\![\Gamma \vdash {\bf pure \:} \langle \pi_1 M, \pi_2 M \rangle : {\bf K}(A \times B)]\!] = & \text{By interpetation} \\
&\eta_{[\![A]\!] \times [\![B]\!]} \circ \langle \pi_1 \circ [\![M]\!], \pi_2 \circ [\![M]\!] \rangle  = & \text{By the property of a product of morphisms} \\
&\eta_{[\![A]\!] \times [\![B]\!]} \circ [\![M]\!] = & \text{By interpetation} \\
&[\![\Gamma \vdash {\bf pure \:} M : {\bf K}(A \times B)]\!]&
\end{array}$

3) $[\![\vdash {\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N : {\bf }K A ]\!] = [\![\vdash {\bf pure \:} N : {\bf K A}]\!]$.

$\begin{array}{lll}
&[\![\vdash {\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N : {\bf }K A ]\!] = & \text{By interpetation}\\
&\mathcal{K}([\![N]\!]) \circ \eta_{\mathds{1}} =& \text{Naturality for $\eta$} \\
&\eta_{[\![A]\!]} \circ [\![N]\!] =& \text{By interpretation} \\
&[\![\vdash {\bf pure \:} N : {\bf K} A]\!]& 
\end{array}$
